### 2019-06-18 Manuscript/Data_Repository/Data_Repository.tex

\section*{Regolith Component}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.5\textwidth]{../Figures/regolith_schematic.pdf}
	\caption{A schematic representation of the regolith component in GEOCLIM at steady state. A rock particle leaves the unweathered bedrock with production rate $P$, and transits vertically through a regolith of height $h$. As the rock particle transits through the regolith, some fraction of the weatherable phases in the rock particle ($x$) are dissolved and leaves the regolith column as weathered phases ($W$). The fraction of the weatherable phases in the rock particle that are not dissolved after transiting through the regolith column leaves it via erosion ($E$).}
	\label{fig:regolith_schematic}
\end{center}
\end{figure}

The regolith component of GEOCLIM models the geochemical evolution of a rock particle as it leaves unweathered bedrock and transits through overlying regolith (Fig. \ref{fig:regolith_schematic}). The component is based upon the theoretical model of \citet{Gabet2009a}, in which material enters the regolith through the downward propagation of the weathering front, and leaves the regolith through physical erosion at the land surface and through the transport of dissolved phases by chemical weathering.

The fundamental processes within the regolith component are described by the following system of three equations:

@@

The steady state solution of the regolith component is obtained by setting the left hand side of Equations \ref{eq:1}, \ref{eq:2} and \ref{eq:3} to zero.

@@

Finally, the erosion rate in the regolith component of GEOCLIM uses the parameterization of \citet{Maffre2018a}, which combines the small-scale incision model of \citet{Davy2000a} with the large-scale BQART model of \citet{Syvitski2007a}:

@@

>>>>

\section*{Silicate Weathering Component}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.5\textwidth]{../Figures/regolith_schematic.pdf}
	\caption{A schematic representation of the silicate weathering in GEOCLIM at steady state. A rock particle leaves the unweathered bedrock with production rate $P$, and transits vertically through a regolith of height $h$. As the rock particle transits through the regolith, some fraction of the weatherable phases in the rock particle ($x$) are dissolved and leaves the regolith column as weathered phases ($W$). The fraction of the weatherable phases in the rock particle that are not dissolved after transiting through the regolith column leaves it via erosion ($E$).}
	\label{fig:regolith_schematic}
\end{center}
\end{figure}

The silicate weathering of GEOCLIM models the geochemical evolution of a rock particle as it leaves unweathered bedrock and transits through overlying regolith (Fig. \ref{fig:regolith_schematic}). The component is based upon the theoretical model of \citet{Gabet2009a}, in which material enters the regolith through the downward propagation of the weathering front, and leaves the regolith through physical erosion at the land surface and through the transport of dissolved phases by chemical weathering.

The fundamental processes within the silicate weathering are described by the following system of three equations:

@@

The steady state solution of the silicate weathering is obtained by setting the left hand side of Equations \ref{eq:1}, \ref{eq:2} and \ref{eq:3} to zero.

@@

Finally, the erosion rate in the silicate weathering of GEOCLIM uses the parameterization of \citet{Maffre2018a}, which combines the small-scale incision model of \citet{Davy2000a} with the large-scale BQART model of \citet{Syvitski2007a}:

@@

\section*{Lithology Implementation}

going from GLiM to our lithologic classes.
